---
title: "Statistical Inference Assignment Part 1"
author: "Bernard Akyena"
date: "August 23, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

#Part 1

#Simulations
##Codes compare the distribution of avergaes of 40 exponentials for 1000 simulations

```{r echo = TRUE}

set.seed(145)
lambda <- 0.2
ranexp <- 40

average <- NULL
for(i in 1:1000)
    average <- c(average, mean(rexp(ranexp, lambda)))
```


#Theoretical Mean

```{r echo = TRUE}
lambda ^ -1
```

#Sample Mean

```{r echo = TRUE}
mean(average)
```
There is very samll difference between the both means


#Theoretical Variance

```{r echo = TRUE}
(lambda * sqrt(ranexp)) ^ -2
```


#Sample Variance

```{r echo = TRUE}
var(average)
```
 The variances exhibit very small differences
 
 
#Distribution

```{r echo = TRUE}
library(ggplot2)
m <- ggplot(data.frame(column = average), aes(x = column))
m <- m + geom_histogram(aes(y = ..density..), binwidth = 0.2, fill = 'blue', color = 'black')
m <- m + stat_function(fun = dnorm, args = list(mean = lambda^-1, sd=(lambda*sqrt(ranexp))^-1), size=2)
m <- m + labs(title = "Distribution of Exponentials", x = "Simulation Means", y = "Density")
m
```
Per the perfect overlay of the normal distribution on the histogram, we can conclude that the distribution of averages
of a large samples of exponentials is really normal
